Asthma Cohort Analytic Epidemiology

### 2017-12-13 r_scripts/analysis/asthma_cohort_analytic_epi.Rmd
finished function. consider adding day of week in future iterations.

# time stratified function; sets up referent observations
ts_casecross <- function(data, start_date, end_date, id, 
                         admit_date, interval){
 data <- ed_cases 
 sym
 # extract id and admit date
 if(id == T){

 }

}

>>>>

# time stratified function; sets up referent observations
time.stratified <- function(data, id, covariate=F, admit_date, 
                            start_date, end_date, interval){
  # if id value is given
  if(is.character(id)){
    # vector of ids
  id_vec <- data[,id]
    } else { # else if no value provided, create an id variable
      id_vec <- seq(1, nrow(data), by=1)
  }
  # vector of admit dates joined to the id vector
  admit_date <- data[,admit_date]
  id_date <- data.frame(id_vec, admit_date)

  # create list of vectors of referent dates and admission date
  referent_date_list <- apply(id_date, 1, function(x){
    date_prior <- as.character(seq(as.Date(x[2]), as.Date(start_date), by = (-interval)))
    date_posterior <- as.character(seq(as.Date(x[2]), as.Date(end_date), by = (interval)))
    date <- sort(unique(c(date_prior, date_posterior)))
    identifier <- rep(x[1], length(date))
    # outcome
    outcome <- ifelse(date %in% x[2], 1, 0)
    id_date_vec <- cbind(identifier, date, outcome)
    return(id_date_vec)
  }) # end apply
    # timestrat dataframe
    ts_data <- do.call(rbind, referent_date_list)
    rownames(ts_data) <- NULL
    ts_data <- as.data.frame(ts_data)
    # if covariates provided, join to the dataframe
    if(is.character(covariate)){
      cov_data <- data[,c(id,covariate)]
      ts_data <- merge(ts_data, cov_data, by.x = "identifier", by.y = id[])
    }
  # return dataframe
  return(ts_data) 
}
